Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-07-05 paper_jasa.tex
listed lineups chosen for follow-up eye-tracker experiment

There are some noticeable exceptions to this rule. In experiment 1, when $\beta=5, n=300, sd=12, rep=3$, people tended to pick the plot with the second smallest $p$-value.  Same experiment, when $\beta=0, n=100, sd=5, rep=1$ people overwhelming chose a plot with much larger $p$-value. For several of these exceptions, along with several easy lineups, we followed up with a new experiment using an eye-tracker to examine what the observers were looking at in making their choices. \cite{*** yifan's CC needs to be made into a tech report, and referenced here.}

>>>>

There are some noticeable exceptions to this rule. In experiment 1, when $\beta=5, n=300, sd=12, rep=3$, people tended to pick the plot with the second smallest $p$-value.  Same experiment, when $\beta=0, n=100, sd=5, rep=1$ people overwhelming chose a plot with much larger $p$-value. For several of these exceptions, along with several easy lineups, we followed up with a new experiment using an eye-tracker to examine what the observers were looking at in making their choices. \cite{*** yifan's CC needs to be made into a tech report, and referenced here.}
Lineups chosen for the follow up eye-tracker experiment were (experiment 1) (1) $n=100, \beta=3, \sigma=5$, rep=1 (2) $n=100, \beta=5, \sigma=5$, rep=1 (3) $n=100, \beta=10, \sigma=12$, rep=1 and (4) $n=300, \beta=5, \sigma=5$, rep=1, and  (experiment 2) (5) $n=100, \beta=3.5, \sigma=12$, rep=1 (6) $n=100, \beta=4.5, \sigma=12$, rep=2 (7) $n=300, \beta=1, \sigma=5$, rep=1 and (8) $n=300, \beta=1, \sigma=5$, rep=2.
